Automated detections reveal the social information in the changing infant view

### 2020-08-24 writeup-paper/draft_apa_blinded.tex
latest paper draft

Correspondence concerning this article should be addressed to Bria L. Long, 450 Serra Mall, Stanford CA 94305. E-mail: bria@stanford.edu}
\keywords{Postural developments, headcam, social information, face detection, pose detection\newline\indent Word count: XXX}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}

@@

\abstract{
Social information plays a key role in infants' early linguistic and
cognitive development. Yet infants locomotor abilities also develop
continuously as they learn to sit, crawl, stand, and walk. How do these
postural developments affect infants access to the social information
relevant for early learning? To address this question, we first created
a rich annotated dataset of naturalistic play sessions between infants
and their caregivers with sets of novel and familiar toys (N=36, 8-16
months of age), recording both egocentric and third-person video. We
then developed an automated analysis method using a pose detection model
(Zhang et al., 2017) to detect the faces and hands in the infant view,
allowing us to analyze the entirety of this dataset. We found that
infants' posture and orientation to their caregiver changed dramatically
across this age range and modulated infants access to social
information; infants who were sitting or standing with their caregiver
at a close distance tended to have the most faces and hands in their
visual field. We also applied our automated method to a second
egocentric video dataset where one-year-olds explored a large play room
with their caregivers (Franchak et al., 2017), replicating and extending
their findings. Together, these results establish the validity of a new
method for detecting social information and confirm that motoric
developments play a significant role in shaping the social information
that infants have access to. We propose that the combined use of
head-mounted cameras and the application of new computer vision
techniques is a promising avenue for re-utilizing rich video datasets
and understanding how the statistics of infants' visual and linguistic
experience change over development.
}

@@

From their earliest months, infants are deeply engaged in learning from
others. Even newborns tend to prefer to look at faces with direct
vs.~averted gaze (Farroni, Csibra, Simion, \& Johnson, 2002) and young
infants follow overt gaze shifts (Bruner, 1975; Gredeback, Fikke, \&
Melinder, 2010). And as infants reach their first birthday, they also
tend to follow (Yu \& Smith, 2013, 2017) and imitate the gestures of
their caregivers (e.g., pointing).

Infants ability to process these social cues may provide strong
scaffolding for early word learning. Longitudinal studies provide some
evidence for this link: children's level of joint engagement with their
mother at 9-12 months predicts both their receptive and productive
vocabularies (Carpenter, Nagell, \& Tomasello, 1998) and 10 month-olds
who follow an adult's gaze (in an experimental context) have larger
vocabularies at 18 months and throughout the second year of life (Brooks
\& Meltzoff, 2005, 2008). While the relationship between hand-following
and language development has been less well characterized, infants who
follow their caregivers' hands tend to be those who spend more time
jointly attending to events with their caregivers (Yu \& Smith, 2017).

Relatively little work, however, has quantified how often infants see
and use these kinds of social cues in naturalistic learing environments.
By using head-mounted cameras to record what infants see, researchers
have begun to document the infant egocentric perspective (Yoshida \&
Smith, 2008) and to quantify the information -- social and otherwise --
available to infants as they learn. While head-mounted camera data do
not provide explicit information on where infants are attending, some
work suggests that infants orient their head towards what they are
focusing on -- putting those people or objects in view (Yoshida \&
Smith, 2008). Initial recordings using this technique during in-lab play
sessions revealed a different view than many imagined: instead of being
dominated by faces, the infant perspective contained close up views of
primarily toys and hands (Franchak, Kretch, Soska, \& Adolph, 2011;
Yoshida \& Smith, 2008; Yu \& Smith, 2017). Subsequent research has
revealed that the infant view is far from a unitary construct,
undergoing dramatic changes as infants grow. Recordings from home
environments suggest that the viewpoints of very young infants -- less
than 4 months of age -- do indeed contain persistent and frequent views
of faces (Fausey, Jayaraman, \& Smith, 2016; Jayaraman, Fausey, \&
Smith, 2017) but that the infant view tends to contain more and more
hands as infants grow older.

These changes in perspective are likely the downstream consequence of a
myriad factors, chief of which may be infants' evolving locomotive
abilities: an infant's ability to sit, crawl, stand, or walk structures
the way they interact with the things and people in their world.
Infants' locomotive abilities can change rapidly: the physical body of
an infant can lengthen up to 2cm in 24 hours (Lampl, 1993), leading to
changes in their physical abilities from one day to the next. These
motoric developments can be thought of as gateways that open up entirely
new phases of development (Iverson, 2010), and cause a cascade of
changes in infants ability to interact with their world and the people
in it (Karasik, Tamis-LeMonda, \& Adolph, 2014).

Thus, infants' changing locomotor abilities may shape the social cues
that infants' see and seek out, in turn impacting their cognitive and
linguistic abilities. Supporting this idea, infants experience with
sitting predicts their success at 3D object completion tasks (Soska,
Adolph, \& Johnson, 2010) as well as their receptive vocabulary
(Libertus \& Violi, 2016). And as children begin crawling (Adolph,
Vereijken, \& Denny, 1998) -- or scooting or cruising (Patrick, Noah, \&
Yang, 2012) -- they are no longer constrained to the same spot that
their caregivers last placed them in. Yet while crawlers can choose
where to go and what they see to a much greater degree, they also appear
to spend much of their time in a world populated by floors and knees;
during spontaneous play, toddlers are more likely to look at the floor
while crawling than while walking (Franchak et al., 2011), when they
have full visual access to their environment and the people in it
(Kretch, Franchak, \& Adolph, 2014).

On one view, it is children's ability to stand and walk that
fundamentally changes their ability to access social information (e.g.,
facial expressions, gaze cues, pointing) relative to children who are
still crawling and sitting (Walle, 2016). In turn, this ability to
access more detailed social information could allow infants to learn
words quicker and more efficiently, facilitating language growth (Walle,
2016). Supporting this idea, walking infants make different kinds of
object-related bids for attention from their caregivers than crawling
infants, and tend to hear more action directed statements (e.g.,
\enquote{open it}) (Karasik et al., 2014); further, in an observational
study, Walle and Campos (2014) also found that children who were able to
walk had both higher receptive and productive vocabularies. However, not
all evidence supports this view: some parental report data suggest a
weak relationship between walking and the onset of language (Moore,
Dailey, Garrison, Amatuni, \& Bergelson, 2019), and head-mounted
eye-tracking data have highlighted the role of infants' in-the-moment
posture -- and that of their caregivers' -- in what infants' see,
finding that these factors are better predictors of the social
information in view than their locomotor status per se (i.e.,
\enquote{walker} vs \enquote{crawler}) (Franchak, Kretch, \& Adolph,
2017).

Understanding this nuanced relationship between the social information
in the infant view and their motoric and linguistic development has
remained challenging. Indeed, different kinds of play sessions (e.g.,
exploring novel environments vs.~playing with novel objects) might
modulate the degree to which infants' posture changes the social
information in view. Furthermore, no work to date has directly examined
how the availability of social information changes in naturalistic
language learning contexts. For example, it is unclear if and how the
social information in view changes during the naming events for
different objects (e.g, \enquote{Look, a {[}ball{]}}).

More broadly, the field is in need of computational tools to reutilize
rich video datasets and to understand the generalizability of findings
across different populations, tasks, and age-ranges. While the field has
assembled many head-mounted camera datasets, conducting new analyses on
these videos has remained prohibitively time-consuming due to a lack of
computational tools for annotations. Instead, hundreds of hours of
manual annotations have been required to analyze a fraction of the
available frames for a given analysis. Thus, despite containing a wealth
of information about the structure of parent-child interactions, these
datasets have thus gone dramatically underused.

Recent innovations in computer vision hold promise for automated
annotations of the infant view. Over the past decade, deep neural
networks have become dramatically better at a wide range of visual
tasks, including object classification, Simonyan and Zisserman
(2014){]}, scene categorization (Zhou, Lapedriza, Khosla, Oliva, \&
Torralba, 2017), and pose detection (K. Zhang, Zhang, Li, \& Qiao,
2016), arguably facilitating our understanding of visual perception
(Peterson, Abbott, \& Griffiths, 2018, VanRullen (2017)) and improving
computational neuroscience (Kietzmann, McClure, \& Kriegeskorte, 2018).
However, as most models have been trained on photographs or videos taken
from the adult perspective, it is still unclear how easily these models
can be applied to videos taken from the infant perspective.

In this paper, we thus first validate a model for the automated
detection of faces and hands in the infant view, using a open-source
model of pose detection -- OpenPose(Cao, Simon, Wei, \& Sheikh, 2017; K.
Zhang et al., 2016) -- that provides pose, face, and hand keypoints for
every person in an image. We compare the detection accuracy of OpenPose
with that of both older and more specialized models of face detection
and demonstrate the usability of this off-the-shelf model for
quantifying the faces and hands in the infant view.

We then apply this automated method to a head-mounted camera dataset
collected in our lab to directly examine the role of postural
developments on the social information in the infant view during
language learning. Specifically, we constructed a dataset where infants
and caregivers played freely using a set of novel and familiar objects;
8, 12, and 16 months-olds (N=36; N=12 in each age group) participated to
ensure a wide range of locomotor abilities. Infants' in-the-moment
posture and orientation relative to their caregiver were hand annotated
and all play sessions were transcribed. This cross-sectional design thus
allowed us to directly examine the relative contributions of age
vs.~postural developments on children's visual access to social
information, and how the avaliability of social cues changes relative to
naming events (e.g., \enquote{Yes, you like the {[}ball!{]}}). Broadly,
we predicted that there would be differential access to social
information based on children's postural developments: crawling infants
would see fewer faces/hands because they would primarily be looking at
the ground, while walking toddlers would have access to a richer visual
landscape with greater access to the social information in their
environment.

To examine the robustness of our automated method and the
generalizability of our findings, we applied OpenPose (Cao et al., 2017)
to the dataset collected in Franchak et al. (2017), where one-year-olds
wore head-mounted eye-tracking cameras during a play session and their
in-the-moment posture was hand-annotated. Unlike the present dataset,
infants and caregivers roamed a large, open playroom and explored
different toys placed throughout. We thus analyzed this dataset with the
goal of both (1) validating our automated method on a very different
kind of dataset, attempting to replicate their primary findings
originally obtained with a head-mounted eye-tracker (2) examining
whether the proportion of hands in view also varies with infants'
posture in an exploratory play session.

\section{Methods}\label{methods}

\subsection{Free-play video dataset}\label{free-play-video-dataset}

A primary goal of this project was to provide a annotated, open dataset
for other researchers to examine the effects of postural developments
and labeling behavior during naturalistic parent-child interactions. We
thus invited caregivers of 8, 12, and 16-month-olds to participate in
play sessions where they were provided with pairs of novel and familiar
objects (e.g., a ball and a microfiber duster, called a \enquote{zem})
in a small playroom in a lab (approximately 10' x 10'). Infants wore
head-mounted cameras equipped with a fish-eye lens (see Head-mounted
camera), a tripod-mounted camera captured a third-person view of the
play session. Using these video data, infants' posture and orientation
to their caregiver were hand-coded and annotated for the entirety of the
play session. All videos were transcribed, and MacArthur CDIs were
collected for all children who particpated. All materials have been made
publicly avaliable on Databrary for whom the parents provided sharing
consent (29/36 dyads) via \url{https://nyu.databrary.org/volume/101}

@@

We used a head-mounted camera (\enquote{headcam}) that was constructed
from a small camera attached to a soft elastic headband.\footnote{Detailed
  instructions for creating this headcam can be found at
  \url{http://babieslearninglanguage.blogspot.com/2013/10/how-to-make-babycam.html}.}
Initial participants wore an MD-80 camera, which was then replaced by a
Veho pro camera which had better battery life and a larger view angle.
The view angle of the MD-80 camera was \(32^{\circ}\) horizontal by
\(24^{\circ}\) vertical, and we attached a fish-eye lens to the camera
to increase the view angle to \(64^{\circ}\) horizontal by
\(46^{\circ}\) vertical. The view angle of the Veho pro camera was
wider, \(47^{\circ}\) horizontal by \(36^{\circ}\) vertical. Videos
captured by MD-80/Veho cameras were 640x480/720x480 pixels,
respectively, and both cameras had a frame rate of \textasciitilde{}30
frames per second. To ensure taht detections across these different
cameras were comparable, we excluded detections from the outer edges of
the videos taken with the MD-80 cameras based on these view angle
differences in our main analyses (i.e.~excluding top/bottom 13\% of the
frames, and left/right 10\% of the frames).

However, the vertical field of view of the cameras were still
considerably reduced compared to the infants' field of view, which spans
around 100--120\(^{\circ}\) in the vertical dimension by 6-7 months of
age (Cummings, Van Hof-Van Duin, Mayer, Hansen, \& Fulton, 1988; Mayer,
Fulton, \& Cummings, 1988). As we were primarily interested in the
presence of faces in the child's field of view, we chose to orient the
camera upwards to capture the entirety of the child's upper visual field
where the child is likely to see adult faces, understanding that this
decision limited our ability to detect hands (especially those of the
child, which are typically found at the bottom of the visual field).

@@

We created custom annotations to describe the child's physical posture
(i.e.~standing) and the orientation of the caregiver relative to the
child (e.g.~far away). The child's posture was categorized as being
carried, prone (crawling or lying), sitting, or standing. The
caregiver's orientation was characterized as being close, far, or behind
the child (independent of distance). For the first two annotations
(close/far from the child), the caregiver could either be to the front
or side of the child. All annotations were made by a trained coder using
the OpenSHAPA/Datavyu software (Adolph, Gilmore, Freeman, Sanderson, \&
Millman, 2012). Times when the child was out of view of the tripod
camera were marked as uncodable and were excluded from these
annotations; similarily, times when the child was being carried or the
caregivers were out of the frame were marked as uncodable for caregiver
orientation. On average, posture or orientation was uncodable from 1-2
minutes of data in each child (seconds excluded from analysis for
posture, M = 104.99s, SD = 233.86s; orientation; M = 104.99s, SD =
233.86s), and these rates did not vary substantially with the age of the
child. To assess the reliability of these annotations, a second coder
annotated videos from three different children to calculate Cohen's
kappa (posture, irr = .82; caregiver orientation, irr = .73).

@@

Viola Jones, the first face detection system, made use of a series of
Haar feature-based cascade classifiers (Viola \& Jones, 2004) applied to
each individual frame. The second algorithm (based on work by K. Zhang
et al. (2016)) uses multi-task cascaded convolutional neural networks
(MTCNNs) for joint face detection and alignment, built to perform well
in real-world environments where varying illuminations and occlusions
are present. We used a Tensorflow implementation of this algorithm
available at \url{https://github.com/davidsandberg/facenet}.

@@

\section{Results}\label{results}

First, we report the accuracy of the automated detectors, as assessed by
comparison to hand-labelled frames from the free-play video dataset
described above. We then apply one of these automated detectors
(OpenPose) to the entirety of this video dataset, and use these outputs
to examine how postural developments influence children's visual access
to faces and hands from 8-16 months of age, as well as how access to
these social cues changes during labeling events (e.g., do you see the
{[}zem{]}?). Finally, we apply this same automated detector to another
video dataset (Franchak et al., 2017), replicating and extending their
findings on the effects of posture on visual access to social
information.

@@

\subsection{Accuracy of automated
detections}\label{accuracy-of-automated-detections}

For face detection, we found that both OpenPose and MTCNN dramatically
outperformed ViolaJones, our baseline model, especially with respect to
the random sample, where ViolaJones missed many face that were in view.
When considering only the composite F-score across all frames, MTCNN
slightly outperformed OpenPose (0.89 MTCNN vs.~0.83 OpenPose), and MTCNN
and OpenPose performed comparably with the random sample. Generally,
MTCNN exhibited higher precision, whereas OpenPose exhibited higher
recall, and these differences were most pronounced on the randomly
sample frames. In other words, while OpenPose generated slightly more
false positives than MTCNN, MTCNN missed several faces that were
accurately detected by OpenPose. When we restricted our analysis to
high-confidence detections from OpenPose (\textgreater{}.5 confidence;
default threshold for visualization), we found very high precision (P =
0.97), but much lower recall (R = 0.64) and thus overall performance (F
= 0.77), indicating that these low-confidence detections often indexed
actual faces that were in the infant view. Figure
\ref{fig:exampledetections} shows example successful detections from
OpenPose in each age group, and Figure \ref{fig:failures} shows examples
of missed faces as well as false positives for context.

We next assessed the viability of OpenPose as a hand detector. Despite
the fact that hand detection is a more computationally challenging
problem (Bambach, Crandall, Smith, \& Yu, 2017), and the fact that we
used wrist keypoints as a proxy for hands, OpenPose performed moderately
well as a hand detector (F = 0.73). OpenPose achieved relatively high
precision -- generating relatively few false positives -- but showed low
recall on the randomly sampled frames (see Table 1). As with face
detections, when we restricted our analysis to high-confidence
detections, we found much higher precision (P = 0.95), but much lower
recall (R = 0.36) and thus overall performance (F = 0.52).

@@

\subsection{Study 1: Access to social information during postural
developments}\label{study-1-access-to-social-information-during-postural-developments}

@@

We directly examined the contributions of posture and orientation
vs.~age by fitting a reduced version of the full model (Nakagawa \&
Schielzeth, 2013) without their fixed effects (both models were run with
the maximal random effects structure). The fixed effects in a model with
only the age of the participants accounted for relatively little
variance in the proportion of faces (marginal \(R^2\) \textless{} 0.01)
or hands in view (marginal \(R^2\) = 0.02). However, when adding
infants' posture and orientation to their caregiver to the model (and
their interaction) the marginal \(R^2\) were higher for both faces
(marginal \(R^2\) = 0.25) and wrists (marginal \(R^2\) = 0.26). Overall,
these results suggest that infants' visual access to social information
is largely modulated by their posture and orientation to their
caregiver, which is in turn a function of their general locomotor
development.

>>>>

Correspondence concerning this article should be addressed to Bria L. Long, 450 Serra Mall, Stanford CA 94305. E-mail: bria@stanford.edu}
\keywords{Postural developments, headcam, social information, face detection, pose detection\newline\indent Word count: 7324}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}

@@

\abstract{
•We provided a open, annotated dataset of naturalistic parent-child
interactions during a play session with with novel and familiar toys,
recording the egocentric and third-person views.

•We develop a novel method using a pose detection model to automatically
quantify the faces and hands in the infant view.

•We apply our novel method to this and another egoecentric video
dataset, and confirm that locomotive developments around the first
birthday shape the faces and hands that infants see in naturalistic
interactions.

•The combined use of head-mounted cameras and automated analyses has the
potential to reveal the changing statistics of the information in the
infant view.

Social information plays a key role in infants' early linguistic and
cognitive development. Yet infants locomotor abilities also develop
continuously as they learn to sit, crawl, stand, and walk. How do these
postural developments affect infants access to the social information
relevant for early learning? To address this question, we first created
a rich annotated dataset of naturalistic play sessions between infants
and their caregivers with sets of novel and familiar toys (N=36, 8-16
month-olds), recording both egocentric and third-person video. We then
developed an automated analysis method using a pose detection model to
detect the faces and hands in the infant view. We found that infants'
posture and orientation to their caregiver changed dramatically across
this age range and modulated infants access to social information;
infants who were sitting or standing with their caregiver at a close
distance tended to have the most faces and hands in their visual field.
We applied this automated method to a second egocentric video dataset
from a previous study, replicating and extending their findings on the
influence of infants' posture on the social information in view.
Together, these results establish the validity of a new method for
detecting social information in egocentric videos and confirm that
motoric developments play a significant role in shaping the social
information that infants have access to. The combined use of
head-mounted cameras and new computer vision techniques is a promising
avenue for understanding how the statistics of infants' visual and
linguistic experience change over development.
}

@@

From their earliest months, infants are deeply engaged in learning from
others. Even newborns tend to prefer to look at faces with direct
vs.~averted gaze (Farroni, Csibra, Simion, \& Johnson, 2002) and young
infants follow overt gaze shifts (Bruner, 1975; Gredeback, Fikke, \&
Melinder, 2010). And as infants reach their first birthday, they also
tend to follow (Yu \& Smith, 2013, 2017) and imitate the gestures of
their caregivers (e.g., pointing). Infants ability to process these
social cues may provide strong scaffolding for early word learning.
Longitudinal studies provide some evidence for this link: children's
level of joint engagement with their mother at 9-12 months predicts both
their receptive and productive vocabularies (Carpenter, Nagell, \&
Tomasello, 1998) and 10 month-olds who follow an adult's gaze (in an
experimental context) have larger vocabularies at 18 months and
throughout the second year of life (Brooks \& Meltzoff, 2005, 2008).
While the relationship between hand-following and language development
has been less well characterized, infants who follow their caregivers'
hands tend to be those who spend more time jointly attending to events
with their caregivers (Yu \& Smith, 2017).

Relatively little work, however, has quantified how often infants see
and use these kinds of social cues in naturalistic learning
environments. By using head-mounted cameras to record what infants see,
researchers have begun to document the infant egocentric perspective
(Yoshida \& Smith, 2008) and to quantify the information -- social and
otherwise -- available to infants as they learn. While head-mounted
camera data do not provide explicit information on where infants are
attending, some work suggests that infants orient their head towards
what they are focusing on -- putting those people or objects in view
(Yoshida \& Smith, 2008). Initial recordings using this technique during
in-lab play sessions revealed a different view than many imagined:
instead of being dominated by faces, the infant perspective contained
close up views of primarily toys and hands (Franchak, Kretch, Soska, \&
Adolph, 2011; Yoshida \& Smith, 2008; Yu \& Smith, 2017). Subsequent
research has revealed that the infant view undergoes dramatic changes as
infants grow. Recordings from home environments suggest that the
viewpoints of very young infants -- less than 4 months of age -- do
indeed contain persistent and frequent views of faces (Fausey,
Jayaraman, \& Smith, 2016; Jayaraman, Fausey, \& Smith, 2017) but that
the infant view tends to contain more and more hands as infants grow
older.

These changes in perspective are likely the downstream consequence of
myriad factors, chief of which may be infants' evolving locomotive
abilities: an infant's ability to sit, crawl, stand, or walk structures
the way they interact with the things and people in their world.
Infants' locomotive abilities can change rapidly: the physical body of
an infant can lengthen up to 2cm in 24 hours (Lampl, 1993), leading to
changes in their abilities from one day to the next. These motoric
developments can be thought of as gateways that open up entirely new
phases of development (Iverson, 2010), causing a cascade of changes in
an infant's ability to interact with their world and the people in it
(Karasik, Tamis-LeMonda, \& Adolph, 2014). Thus, infants' changing
locomotor abilities may shape the social cues that infants' see and seek
out, in turn impacting their cognitive and linguistic abilities.

However, understanding the nuanced relationship between the social
information in the infant view and their motoric and linguistic
development has remained challenging. For example, as children begin
crawling (Adolph, Vereijken, \& Denny, 1998) -- or scooting or cruising
(Patrick, Noah, \& Yang, 2012) -- they are no longer constrained to the
same spot that their caregivers last placed them in. Yet while crawlers
can choose where to go and what they see to a much greater degree, they
also appear to spend much of their time in a world populated by floors
and knees; during spontaneous play, toddlers are more likely to look at
the floor while crawling than while walking (Franchak et al., 2011),
when they have full visual access to their environment and the people in
it (Kretch, Franchak, \& Adolph, 2014). Further, infants' experience
with sitting predicts their success at 3D object completion tasks
(Soska, Adolph, \& Johnson, 2010) as well as their receptive vocabulary
(Libertus \& Violi, 2016), suggesting the importance of focused play
sessions for language development.

Others have posited that it is children's ability to stand and walk that
fundamentally changes their ability to access social information (e.g.,
facial expressions, gaze cues, pointing) relative to children who are
still crawling and sitting (Walle, 2016), which in turn allow infants to
learn words quicker and more efficiently (Walle, 2016). Supporting this
idea, walking vs.~crawling infants tend to make different kinds of
object-related bids for attention from their caregivers (Karasik et al.,
2014), hear more action directed statements (e.g., \enquote{open it})
(Karasik et al., 2014), and have higher receptive and productive
vocabularies (Walle \& Campos, 2014). However, not all evidence supports
this view: parental report data suggest a weak relationship between
walking and the onset of language (Moore, Dailey, Garrison, Amatuni, \&
Bergelson, 2019), and head-mounted eye-tracking data from one-year-olds
highlights the role of infants' in-the-moment posture -- and that of
their caregivers' -- in what infants' see, finding that these factors
are better predictors of the social information in view than their
locomotor status per se (i.e., \enquote{walker} vs \enquote{crawler})
(Franchak, Kretch, \& Adolph, 2017).

Broadly, the field is in need of computational tools to reuse these rich
video datasets and understand the generalizability of findings across
different populations, tasks, and age-ranges. For example, different
kinds of play sessions (e.g., exploring novel environments vs.~playing
with novel objects) might modulate the degree to which infants' posture
changes the social information in view. Yet while the field has
assembled many head-mounted camera datasets, conducting new analyses on
these videos has remained prohibitively time-consuming due to a lack of
computational tools for annotations. Instead, hundreds of hours of
manual annotations have been required to analyze a fraction of the
available frames for a given analysis. Thus despite containing a wealth
of information about the structure of parent-child interactions, these
datasets have thus gone dramatically underused.

Recent innovations in computer vision hold promise for automated
annotations of the infant view. Over the past decade, deep neural
networks have become dramatically better at a wide range of visual
tasks, including object classification, Simonyan and Zisserman (2014),
scene categorization (Zhou, Lapedriza, Khosla, Oliva, \& Torralba,
2017), and pose detection (K. Zhang, Zhang, Li, \& Qiao, 2016), arguably
facilitating our understanding of visual perception (Peterson, Abbott,
\& Griffiths, 2018; VanRullen, 2017) and improving computational
neuroscience (Kietzmann, McClure, \& Kriegeskorte, 2018). However, as
most models have been trained on photographs or videos taken from the
adult perspective, it is still unclear how easily these models can be
applied to videos taken from the infant perspective.

In the present paper, we make progress on understanding the relationship
the between the infant visual perspective and motoric and linguistic
development in three ways. First, we validate a model for the automated
detection of faces and hands in the infant view. We use an open-source
model of pose detection -- OpenPose (Cao, Simon, Wei, \& Sheikh, 2017;
K. Zhang et al., 2016) -- that provides pose, face, and hand keypoints
for every person in an image. We compare the detection accuracy of this
method with that of both older and more specialized models of face
detection, and demonstrate the usability of this off-the-shelf model for
quantifying the faces and hands in the infant view.

Second, we provide an annotated, open dataset for researchers to examine
the effects of postural developments and naming behavior during
naturalistic parent-child interactions. To do so, we invited caregivers
of 8, 12, and 16-month-olds to participate in play sessions where they
were provided with pairs of novel and familiar objects (e.g., a ball and
a microfiber duster, called a \enquote{zem}). We chose this age-range to
span the months when infants typically transition from sitting to
crawling to standing, and documented the infant egocentric view as well
as a third-person view of the play session. We then annotated infants'
in-the-moment posture and orientation relative to their caregiver, and
obtained full transcripts of the play sessions as well as
MacArthur-Bates Communicative Development Inventories for each child.

Third, we apply our automated method to this and one other openly
available head-mounted camera dataset, examining the generality of the
effects of motor development on the social information in view. In Study
1, we use the cross-sectional design of our dataset to directly examine
the relative contributions of age vs.~in-the-moment posture on infants'
visual access to social information, and use the transcriptions to
examine how the availability of social cues changes relative to naming
events (e.g., \enquote{Yes, you like the {[}ball!{]}}). Indeed, despite
positing links between the social information in view and language
development, no work to date has directly examined how the availability
of social information changes around naming events in naturalistic
contexts. In Study 2, we apply this automated method to Franchak et al.
(2017), where one-year-olds wore head-mounted eye-tracking cameras
during a play session and their in-the-moment posture was
hand-annotated. Unlike the present dataset, infants and caregivers
roamed a large, open playroom and explored different toys placed
throughout. We thus analyzed this second dataset with a first goal of
validating our automated method on a very different kind of video
dataset, attempting to replicate their primary findings originally
obtained with a head-mounted eye-tracker, and then further examine
whether the proportion of hands in view also varies with infants'
posture. Broadly, we predicted that there would be differential access
to social information based on children's postural developments:
crawling infants would see fewer faces/hands because they would
primarily be looking at the ground, while walking toddlers would have
access to a richer visual landscape with greater access to the social
information in their environment.

\section{Study 1}\label{study-1}

\subsection{Methods}\label{methods}

Caregivers of 8, 12, and 16-month-olds were invited to participate in
play sessions where they were provided with pairs of novel and familiar
objects (e.g., a ball and a microfiber duster, called a \enquote{zem})
in a small playroom in a lab (approximately 10' x 10'). Infants wore
head-mounted cameras equipped with a fish-eye lens (see Head-mounted
camera), a tripod-mounted camera captured a third-person view of the
play session. Using these video data, infants' posture and orientation
to their caregiver were hand-coded and annotated for the entirety of the
play session. All videos were transcribed, and MacArthur CDIs were
collected for all children who participated. All materials have been
made publicly available on Databrary for whom the parents provided
sharing consent (29/36 dyads) via {[}BLINDED{]}.

@@

We used a head-mounted camera (\enquote{headcam}) that was constructed
from a small camera attached to a soft elastic headband.\footnote{Detailed
  instructions for creating this headcam can be found at {[}BLINDED{]}.}
Initial participants wore an MD-80 camera, which was then replaced by a
Veho pro camera which had better battery life and a larger view angle.
The view angle of the MD-80 camera was \(32^{\circ}\) horizontal by
\(24^{\circ}\) vertical, and we attached a fish-eye lens to the camera
to increase the view angle to \(64^{\circ}\) horizontal by
\(46^{\circ}\) vertical. The view angle of the Veho pro camera was
wider, \(47^{\circ}\) horizontal by \(36^{\circ}\) vertical. Videos
captured by MD-80/Veho cameras were 640x480/720x480 pixels,
respectively, and both cameras had a frame rate of \textasciitilde{}30
frames per second. To ensure that detections across these different
cameras were comparable, we excluded detections from the outer edges of
the videos taken with the MD-80 cameras based on these view angle
differences in our main analyses (i.e.~excluding top/bottom 13\% of the
frames, and left/right 10\% of the frames).

However, the vertical field of view of the cameras were still
considerably reduced compared to the infants' field of view, which spans
around 100--120\(^{\circ}\) in the vertical dimension by 6-7 months of
age (Cummings, Van Hof-Van Duin, Mayer, Hansen, \& Fulton, 1988; Mayer,
Fulton, \& Cummings, 1988). As we were primarily interested in the
presence of faces in the child's field of view, we chose to orient the
camera upwards to capture the entirety of the child's upper visual field
where the child is likely to see adult faces, understanding that this
decision limited our ability to detect hands (especially those of the
child, which are typically found at the bottom of the visual field). We
note that these limitations regarding field of view and camera angle
affect all studies using this method, not only our own.

@@

We created custom annotations to describe the child's physical posture
(i.e.~standing) and the orientation of the caregiver relative to the
child (e.g.~far away). The child's posture was categorized as being
carried, prone (crawling or lying), sitting, or standing. The
caregiver's orientation was characterized as being close, far, or behind
the child (independent of distance). For the first two annotations
(close/far from the child), the caregiver could either be to the front
or side of the child. All annotations were made by a trained coder using
the OpenSHAPA/Datavyu software (Adolph, Gilmore, Freeman, Sanderson, \&
Millman, 2012). Times when the child was out of view of the tripod
camera were marked as uncodable and were excluded from these
annotations; similarily, times when the child was being carried or the
caregivers were out of the frame were marked as uncodable for caregiver
orientation. On average, posture or orientation was uncodable from 1-2
minutes of data in each child (seconds excluded from analysis for
posture, M = 105s, SD = 234s; orientation; M = 105s, SD = 234s), and
these rates did not vary substantially with the age of the child. To
assess the reliability of these annotations, a second coder annotated
videos from three different children to calculate Cohen's kappa
(posture, \(\kappa\) = .82; caregiver orientation, \(\kappa\) = .73).

@@

Viola Jones, the first face detection system, made use of a series of
Haar feature-based cascade classifiers (Viola \& Jones, 2004) applied to
each individual frame. The second algorithm (based on work by K. Zhang
et al., 2016) uses multi-task cascaded convolutional neural networks
(MTCNNs) for joint face detection and alignment, built to perform well
in real-world environments where varying illuminations and occlusions
are present. We used a Tensorflow implementation of this algorithm
available at \url{https://github.com/davidsandberg/facenet}.

@@

\subsection{Results}\label{results}

First, we report the accuracy of the automated detectors, as assessed by
comparison to hand-labelled frames from the free-play video dataset
described above. We then apply one of these automated detectors
(OpenPose) to the entirety of this video dataset, and use these outputs
to examine how postural developments influence children's visual access
to faces and hands from 8-16 months of age. We further use the
detections to examine how access to these social cues changes during
naming events (e.g., do you see the {[}zem{]}?). Finally, we apply this
same automated detector to another video dataset (Franchak et al.,
2017), replicating and extending their findings on the effects of
posture on visual access to social information.

@@

\subsubsection{Accuracy of automated
detections}\label{accuracy-of-automated-detections}

For face detection, we found that both OpenPose and MTCNN dramatically
outperformed ViolaJones (our baseline model) especially with respect to
the random sample, where ViolaJones missed many face that were in view
(see Table 1). When considering only the composite F-score across all
frames, MTCNN slightly outperformed OpenPose (0.89 MTCNN vs.~0.83
OpenPose), and MTCNN and OpenPose performed comparably with the random
sample. Generally, MTCNN exhibited higher precision, whereas OpenPose
exhibited higher recall, and these differences were most pronounced on
the randomly sample frames. In other words, while OpenPose generated
slightly more false positives than MTCNN, MTCNN missed several faces
that were accurately detected by OpenPose. When we restricted our
analysis to high-confidence detections from OpenPose (\textgreater{}.5
confidence; default threshold for visualization), we found very high
precision (P = 0.97), but much lower recall (R = 0.64) and thus overall
lower performance (F = 0.77), indicating that these low-confidence
detections often indexed actual faces that were in the infant view.
Figure \ref{fig:exampledetections} shows example successful detections
from OpenPose in each age group, and Figure \ref{fig:failures} shows
examples of missed faces as well as false positives for context.

We next assessed the viability of OpenPose as a hand detector. Despite
the fact that hand detection is a more computationally challenging
problem (Bambach, Crandall, Smith, \& Yu, 2017), and the fact that we
used wrist keypoints as a proxy for hands, OpenPose performed moderately
well as a hand detector (F = 0.73). OpenPose achieved relatively high
precision -- generating relatively few false positives -- but showed low
recall on the randomly sampled frames (see Table 1). As with face
detections, when we restricted our analysis to high-confidence
detections, we found much higher precision (P = 0.95), but much lower
recall (R = 0.36) and thus lower overall performance (F = 0.52).

@@

@@

We directly examined the contributions of posture and orientation
vs.~age by fitting a reduced version of the full model (Nakagawa \&
Schielzeth, 2013) without their fixed effects (both models were run with
the maximal random effects structure), and comparing model fits for each
of these. The fixed effects in a model with only the age of the
participants accounted for relatively little variance in the proportion
of faces (marginal \(R^2\) \textless{} 0.01) or hands in view (marginal
\(R^2\) = 0.02). However, when adding infants' posture and orientation
to their caregiver to the model (and their interaction) the marginal
\(R^2\) were higher for both faces (marginal \(R^2\) = 0.25) and wrists
(marginal \(R^2\) = 0.26). Overall, these results suggest that infants'
visual access to social information is largely modulated by their
posture and orientation to their caregiver, which is in turn a function
of their general locomotor development.
